A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-22 shanghai.tex
Toward geometric reciprocity for local tori + label inserted.
I started to write up the proof of the result on Weil restriction over local fields, but ran out of time. I'll come back to this when I can.

\begin{proof}
Weil restriction behaves properly with respect to formation of Néron models:
adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} 
gives a canonical isomorphism 
\Clifton{I need to check this.}
\begin{equation}
\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
\end{equation}
And Weil restriction behaves properly with respect to the Greenberg transform:
\Clifton{I'm not so sure about this . . . In fact, I don't believe it!}
\begin{equation}
\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
\iso
\Res_{k'/k} \Gr_n(\underline{T'}),
\end{equation}
where $k'$ is the residue field for $K'$.
And the Greenberg transform respects products:
\[
\Gr_n(\underline{T'}) = \Gr_n(\underline{T}\times_{k} {k'}) \iso \Gr_n(\underline{T})\times_{k} {k'} = \Gr_n(\underline{T})_{k'}.
\]
Thus, the 
Now use Proposition~\ref{prop:csbe}.
\end{proof}

>>>>

\begin{proof}
Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} for lft-Neron models
gives a canonical isomorphism 
\begin{equation}\label{weilneron}
\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
\end{equation}

Weil restriction is also compatible with the Greenberg transform, in the following sense: if $e$ is the ramification degree of $K'/K$ then
\begin{equation}\label{weilgreenberg}
\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
\iso
\Res_{k'/k} \Gr_{en}(\underline{T'}),
\end{equation}
where $k'$ is the residue field for $K'$.
To see this, we employ the functor of points perspective. Let $R$ be any $\Fq$-algebra. Then 
\[
\begin{aligned}
\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
&=
\end{aligned}
\]

\[
\Gr_n(\underline{T'}) = \Gr_n(\underline{T}\times_{k} {k'}) \iso \Gr_n(\underline{T})\times_{k} {k'} = \Gr_n(\underline{T})_{k'}.
\]
Thus, the 
Now use Proposition~\ref{prop:csbe}.
\end{proof}
